Fifteen years of decentralization attempts

### 2014-03-22 paper.tex
changed conclusion

	In this technical report we explained how Tor works and which components define a Tor network. Furthermore, we looked at the main disadvantages and problems Tor is currently facing. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. After that, we've written which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.

	From the decentralization table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor. Decentralized systems that do exist such as Tarzan, I2P, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet. Yet each of these systems either lacks in performance or is vulnerable to some type of attack.

>>>>

	We explained how Tor works and which components define a Tor network. Furthermore, we looked at the main disadvantages and problems Tor is currently facing. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. After that, we've written which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.

	From table \ref{tbl:comparison}, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While a lot of research has been done on decentralized systems, there is no system yet that can compete with Tor. Decentralized systems that do exist such as Tarzan, I2P, Torsk or Gnutella, show promising attempts to decentralize and anonymize the internet. Yet each of these systems either lacks in performance or is vulnerable to some type of attack.
